Weather vanes and runaways: Bow shocks across the HR diagram

### 2018-06-26 papers/Papers1234/sec-dust-bow-intro.tex
Add figure with example magnetic trajectories

@@

We now investigate how the results of the previous sections are
modified by magnetic fields in the tight coupling limit.  For
simplicity, we assume a uniform field in the incoming stream, with
field lines oriented at an angle \(\theta\B\) to the velocity vector that
defines the bow axis.  We also assume a super-alfvénic stream,
\(v_\infty > v\alfven\), so that the radius, \(R_0\), of the wind bow shock
is unaffected, and take \(t_* \ll \tau_{*, \text{max}}\), so that the
back-reaction of the grain drag on the plasma is negligible (see
previous section) and \(B\) remains uniform in magnitude and direction
in the dust wave region, outside of the bow shock.  In
Appendix~\ref{sec:tight-magn-coupl}, we derive results in the limit of
zero gas--grain drag, which is appropriate for inertia-confined dust
waves.

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/frozen-trajectories-multi}
  \caption{Sample grain trajectories for drag-confined dust waves with
    tight magnetic coupling.}
  \label{fig:frozen-trajectories}
\end{figure}

@@

We now investigate how the results of the previous sections are
modified by magnetic fields in the tight coupling limit.  For
simplicity, we assume a uniform field in the incoming stream, with
field lines oriented at an angle \(\theta\B\) to the velocity vector that
defines the bow axis.  We also assume a super-alfvénic stream,
\(v_\infty > v\alfven\), so that the radius, \(R_0\), of the wind bow shock
is unaffected, and take \(t_* \ll \tau_{*, \text{max}}\), so that the
back-reaction of the grain drag on the plasma is negligible (see
previous section) and \(B\) remains uniform in magnitude and direction
in the dust wave region, outside of the bow shock.  In
Appendix~\ref{sec:tight-magn-coupl}, we derive results in the limit of
zero gas--grain drag, which is appropriate for inertia-confined dust
waves, while in Figures~\ref{fig:frozen-stream}
and~\ref{fig:frozen-trajectories} we show example results for
drag-confined dust waves.
